Naturalness in U(1) extensions of the MSSM

### 2015-01-22 paper/e6ssm-tuning-paper.tex
removed comment.

Since the stop mass does not have such a large impact on the fine
tuning when the cutoff scale is very low we can use this to see more
clearly the impact of the $Z^\prime$ mass on fine tuning. To do so we
select a fixed low cutoff of $M_X=20$ TeV and compare the fine tuning
for two different values of the $Z^\prime$ mass. We choose to look at
$M_{Z^\prime}=2.5$ TeV, which is just above the current limits, and
$M_{Z^\prime}=4.5$ TeV, which should be in reach in run II at the LHC
\cite{Godfrey:2013eta} and then compare the fine tuning calculated in
each case to the tuning in the MSSM.  For this, we have performed a
large six dimensional parameter space scan in both the MSSM and
E$_6$SSM, varying those parameters most relevant for the fine tuning
and the Higgs mass.  Therefore the set of parameters which we vary
includes $\mu$, $B$ and $\tan \beta$ for the MSSM, and $\lambda$,
$A_\lambda$ and $\tan \beta$, for the E$_6$SSM, which appear at tree
level in the EWSB conditions of the models. While the RGE contribution
from large stop masses to the fine tuning is small for such a low
cut-off scale, the stop contributions to the effective potential can
play a significant role in reducing the fine tuning [WE SHOULD DISCUSS
  THIS].  For this reason it is still important to properly treat the
tuning associated with stop contributions to the one-loop effective
potential, and so we also scan over the soft masses $m_{Q_3}^2$,
$m_{u_3}^2$ and the stop mixing $A_t$.  The relevant parameters and
ranges that were scanned over are summarised in Table
\ref{tab:scanranges}. With the exception of the stop mixing $A_t$ and
the soft trilinear $A_\lambda$, which are logarithmically scanned, all
parameters are linearly scanned.  In addition to this we also repeat
each scan for three different values of $M_2$ to allow more variation
in the chargino masses.

>>>>

Since the stop mass does not have such a large impact on the fine
tuning when the cutoff scale is very low we can use this to see more
clearly the impact of the $Z^\prime$ mass on fine tuning. To do so we
select a fixed low cutoff of $M_X=20$ TeV and compare the fine tuning
for two different values of the $Z^\prime$ mass. We choose to look at
$M_{Z^\prime}=2.5$ TeV, which is just above the current limits, and
$M_{Z^\prime}=4.5$ TeV, which should be in reach in run II at the LHC
\cite{Godfrey:2013eta} and then compare the fine tuning calculated in
each case to the tuning in the MSSM.  For this, we have performed a
large six dimensional parameter space scan in both the MSSM and
E$_6$SSM, varying those parameters most relevant for the fine tuning
and the Higgs mass.  Therefore the set of parameters which we vary
includes $\mu$, $B$ and $\tan \beta$ for the MSSM, and $\lambda$,
$A_\lambda$ and $\tan \beta$, for the E$_6$SSM, which appear at tree
level in the EWSB conditions of the models. While the RGE contribution
from large stop masses to the fine tuning is small for such a low
cut-off scale, the stop contributions to the effective potential can
play a significant role in reducing the fine tuning.  For this reason it is still important to properly treat the
tuning associated with stop contributions to the one-loop effective
potential, and so we also scan over the soft masses $m_{Q_3}^2$,
$m_{u_3}^2$ and the stop mixing $A_t$.  The relevant parameters and
ranges that were scanned over are summarised in Table
\ref{tab:scanranges}. With the exception of the stop mixing $A_t$ and
the soft trilinear $A_\lambda$, which are logarithmically scanned, all
parameters are linearly scanned.  In addition to this we also repeat
each scan for three different values of $M_2$ to allow more variation
in the chargino masses.
